A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-09-11 src/paper.tex
WIP: Devices communication

\title{A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments}
\author{Ricardo~Erikson~V.~de~S.~Rosa, 
	Vicente~Ferreira~de~Lucena~Jr.,\IEEEmembership{Member,IEEE,}
	and~Lucas~Carvalho~Cordeiro
	%
\thanks{Ricardo Erikson V. de S. Rosa is with the Graduate Program in Electrical Engineering, Federal University of Minas Gerais, Av. Antônio Carlos 6627, 31270-901, Belo Horizonte, MG, Brazil(e-mail: ricardoerikson@ufmg.br)}%
\thanks{Vicente Ferreira de Lucena Jr. is with the PPGEE, PPGI, and CETELI - Electronics and Information Technology R\&D Center at UFAM, Manaus, Amazonas, Brazil (e-mail: vicente@ufam.edu.br)}%
\thanks{Lucas Carvalho Cordeiro is with the PPGEE-UFAM, and CETELI - Electronics and Information Technology R\&D Center, Manaus, Amazonas, Brazil (e-mail:lucascordeiro@ufam.edu.br)}}

@@

\subsection{Experiment}

>>>>

\title{A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments}
\author{Ricardo~Erikson~V.~de~S.~Rosa,\IEEEmembership{Student Member, IEEE,} 
	and Vicente~Ferreira~de~Lucena~Jr.,\IEEEmembership{Senior Member,IEEE}
	% and~Lucas~Carvalho~Cordeiro
	%
\thanks{Ricardo Erikson V. de S. Rosa is with the Graduate Program in Electrical Engineering, Federal University of Minas Gerais, Av. Antônio Carlos 6627, 31270-901, Belo Horizonte, MG, Brazil(e-mail: ricardoerikson@ufmg.br)}%
\thanks{Vicente Ferreira de Lucena Jr. is with the PPGEE, PPGI, and CETELI - Electronics and Information Technology R\&D Center at UFAM, Manaus, Amazonas, Brazil (e-mail: vicente@ufam.edu.br)}%
% \thanks{Lucas Carvalho Cordeiro is with the PPGEE-UFAM, and CETELI - Electronics and Information Technology R\&D Center, Manaus, Amazonas, Brazil (e-mail:lucascordeiro@ufam.edu.br)}
}

@@

An important feature of the architecture described in this paper is the possibility of performing communication between iTV and secondary screen devices. This type of communication enable the discovery of devices that are physically nearby, i.e., devices on the same local network or not. Since people are typically carry their phones with them, it is possible to manage who is present in the environment at a given moment.

Industry provided several means to provide communication among devices.

\section{Experiment: Evaluation of TV Programs using Second Screen}

% Enfatizar a interação de avaliar um programa
